The influence of massive early merger events on the chemo-dynamics of galaxy discs

### 2022-10-18 src/tex/ms.tex
[showyourwork] overleaf sync

@@

\begin{figure}
    \script{merger_ratio.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/2.79e12_merger_ratio_gas.pdf}
        \caption{
            Half mass radius of the cold gas as a function of time. The sharp increases in the cold gas size around 2 Gyr and 9 Gyr indicate the influence of massive gas rich merger events on the galaxy. The addition of fresh cold gass leads to a sudden increase in cold gas half mass size.
        }
        \label{fig:half_mass}
    \end{centering}
\end{figure}

@@

Not sure, we get a high res version done until this paper will be submitted...
Let's try g8.26e11

>>>>

% --- HACK to remove showyourwork abstract margin icon
\makeatletter
\def\abstract{\if@twocolumn
   \start@SFBbox\@abstract
 \else
   \@abstract
 \fi}
\def\endabstract{\if@twocolumn
   \endlist\finish@SFBbox
 \else
  \endlist
 \fi}
\makeatother
% ---

@@

\begin{figure}
    \begin{centering}
        \includegraphics[width=\linewidth]{static/279e12_merger_ratio_gas.pdf}
        \caption{

        }
        \label{fig:merger_ratio}
    \end{centering}
\end{figure}

@@

\begin{figure*}
    \script{age_feh.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/2.79e12_age_metallicity_grid.pdf}
        \caption{
            Age-metallicity relation.
        }
        \label{fig:half_mass}
    \end{centering}
\end{figure*}

\begin{figure*}
    \script{feh_ofe.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/2.79e12_feh_ofe_grid.pdf}
        \caption{
            Oxygen vs. metallicity.
        }
        \label{fig:half_mass}
    \end{centering}
\end{figure*}
